---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# redditapi

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- badges: end -->

Tools to interact with the [Reddit OAuth2 API](https://www.reddit.com/dev/api/) in R.

## Installation

You can install the development version of redditapi from github:

``` r
remotes::install_github("paulc91/redditapi")
```

## Setup Reddit API application

To authenticate to use the OAuth2 API, you need your own application. The following instructions are based on Reddit's [OAuth2 Quick Start Example](https://github.com/reddit-archive/reddit/wiki/OAuth2-Quick-Start-Example) and *will only work for 'script' type apps, which will ONLY have access to accounts registered as "developers" of the app and require the application to know the user's password*.

-   [Create a reddit user account](https://www.reddit.com/register/) (if you don't already have one)

-   [Create API application](https://www.reddit.com/prefs/apps/)

    -   give it a name
    -   select 'script' (an application intended for a single developer)
    -   add a description
    -   provide a redirect URL (this won't actually be used but is required so put something like <http://localhost:8080>)

Once created, note the application client\_id (below the app name) and secret.

## Store credentials as R environment variables

You will need the client id, secret and name (agent) of your API application, as well as your reddit username and password to authenticate in R. It is a good idea to store these as environment variables using an `.Renviron` file either in your home or project directory.

You can generate or edit an `.Renviron` with the `usethis` package function `usethis::edit_r_environ(scope = "user")`. Change the scope to `"project"` to limit the environment variables to the current project you are working in rather than all R sessions for your user.

Add the following to the `.Renviron` file, then save and restart the R session.

    REDDIT_CLIENT_ID=your_client_id_here
    REDDIT_SECRET=your_secret_here
    REDDIT_AGENT=your_app_name_here
    REDDIT_USERNAME=your_username_here
    REDDIT_PASSWORD=your_password_here

## Example usage

### Load package and your API credentials

```{r setup, warning=FALSE, message=FALSE}
library(redditapi)
library(dplyr)

client_id <- Sys.getenv("REDDIT_CLIENT_ID") # the client id of your api application
secret <- Sys.getenv("REDDIT_SECRET") # the secret of your api application
agent <- Sys.getenv("REDDIT_AGENT") # the name of your api application
username <- Sys.getenv("REDDIT_USERNAME") # your personal reddit username
password <- Sys.getenv("REDDIT_PASSWORD") # your personal reddit password
```

### Retrieve a token

```{r}
token <- get_reddit_token(
  agent = agent,
  client_id = client_id,
  secret = secret,
  username = username,
  password = password
)
```

### Retrieve post data from a subreddit

Because we have authenticated and are using the OAuth2 api, you can access private subreddits you are a member of.

-   `limit` is the number of posts to return per page (100 maximum)
-   `max_pages` is the max number of pages to attempt to pull per request

The total number of items returns will be `limit` \* `max_pages`, or all items in the subreddit if that number is lower.

```{r}
# request the 200 most recent posts from the r/ambient music subreddit
posts <- get_reddit_posts(
  subreddit = "ambient", 
  token = token,
  agent = agent, 
  username = username, 
  limit = 100,
  max_pages = 2 
)
```

A data.frame for each page requested is returned inside a list. We can then use `dplyr` to combine all pages together and extract the information we are interested in:

```{r}
posts_df <- 
  bind_rows(posts) %>% 
  as_tibble() %>% 
  select(created_utc, author, title, url, score, num_comments) %>% 
  mutate(created_utc = lubridate::as_datetime(created_utc))

posts_df
```
